MLPPI Wizard: An Automated Multi-level Partitioning Tool on Analytical Workloads

### 2017-03-09 mlppi-comsis17/paper.tex
ComSIS paper

In this section we describe in detail each phase of the wizard using the query set $Q$ \hbox{provided} in Section~\ref{sec:intro}.

@@

Algorithm~\ref{algo:pre_phase} sketches 
the steps in the preprocessing phase. 
This phase consists of a total of six steps.

@@

The first step of this phase is to simplify the predicate(s) of each query 
by removing redundant conditions. 
For instance, if a query predicate has the condition of 
``{\tt LO\_DISCOUNT IN (1, 4, 5) AND LO\_DISCOUNT IN (2, 3, 4, 5)}'', 
then the predicate can be simplified as ``{\tt LO\_DISCOUNT IN (4, 5)}.'' 
This can be done via an API call to the DBMS server. 
In the running example this simplification is not required.

@@

The following step is to gather the simplified predicates and 
then obtain ranges from the collected predicates. 
This can also be done through an API call to the server. 
The query predicate is of the form  
\begin{center}
\begin{tabular}{l} 
\form{\tt variable} \form{\tt op} \form{\tt constant},
\end{tabular}
\end{center}
where \form{\tt variable} is a field from {\tt LINEORDER}, 
\form{\tt op} is in 
\begin{center}
\begin{tabular}{l} 
\{{\tt $ = $ }, {\tt $ < $}, {\tt $ <= $}, {\tt $ >= $}, {\tt $ > $}, 
{\tt IN}\},
\end{tabular}
\end{center}
and \form{\tt constant} represents a constant value(s). 
All \form{\tt op}s are self-explanatory. 
In particular, `{\tt IN}' is a list predicate implying `{\tt OR}' operator.
In the running example, 
we can collect a set of predicates $P$ = \{$p$1,$p$2,$p$3,$p$4\} from $Q$, where

>>>>

As illustrated in Figure~\ref{fig:arch}, 
the MLPPI wizard has the three phases for a final partitioning recommendation. 
In this section we delve into each phase. For better exposition we use the running 
query set $Q$ \hbox{provided} in Section~\ref{sec:intro}.

@@

The first phase is called {\em Preprocessing} 
to extract query predicates and check any constraint in partitioning. 
This phase consists of a total of six steps, as shown in Algorithm~\ref{algo:pre_phase}. 
%We elaborate on each step in the subsequent section.

@@

The first step is to simplify the predicates of queries in a given workload.
In other words, we remove redundant conditions among the queries. 
For instance, if a query predicate has the condition of 
``{\tt LO\_DISCOUNT IN (1, 4, 5) AND LO\_DISCOUNT IN (2, 3, 4, 5)}'', 
then the predicate can be simplified as \linebreak ``\hbox{{\tt LO\_DISCOUNT}} {\tt IN (4, 5)}.'' 
This can be done via an API call to the database server. 
This simplification is not required for the running example.

@@

In the subsequent step we gather the simplified predicates and 
then extract ranges from the collected predicates. 
This task can also be conducted through an API call to the server. 
The query predicate is of the form 
\begin{center}
\begin{tabular}{l} 
\form{\tt variable} \form{\tt op} \form{\tt constant},
\end{tabular}
\end{center}
where \form{\tt variable} is a field from {\tt LINEORDER}, 
\form{\tt op} is in 
\begin{center}
\begin{tabular}{l} 
\{{\tt $ = $ }, {\tt $ < $}, {\tt $ <= $}, {\tt $ >= $}, {\tt $ > $}, 
{\tt IN}\},
\end{tabular}
\end{center}
and \form{\tt constant} represents a constant value(s). 
All \form{\tt op}s are self-explanatory. 
In particular, `{\tt IN}' is a list predicate implying `{\tt OR}' operator.
In the running example, 
we can collect a set of predicates $P$ = \{$p$1,$p$2,$p$3,$p$4\} from $Q$, where
